---
title: "p8105 hw6"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(mgcv)
library(modelr)
library(purrr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%",
  warning = FALSE,
  message = FALSE)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 2 

### Data Cleaning 

```{r}
homicide_df =
  read_csv("./data/homicide-data.csv", na = c("", "Unknown", "NA")) %>% 
  mutate(
    city_state = str_c(city, ", ", state),
    victim_age = as.numeric(victim_age),
    status = if_else(disposition == "Closed without arrest" | disposition == "Open/No arrest", "unresolved", "resolved"),
    status_numeric = if_else(status == "unresolved", 0, 1)
  ) %>% 
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" & city_state != "Kansas City, MO" & city_state != "Tusla, AL") %>% 
  filter(victim_race == "White" | victim_race == "Black")
```

### Logistic Regression Model
```{r}
Baltimore_reg =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(status_numeric ~ victim_race + victim_age + victim_sex, family = binomial(link='logit') , data = .)

Baltimore_reg %>% 
  broom::tidy()
```

### Adjusted odds ratio 
The adjusted odds ratio of solving homicides for male victim compared to female victim is 0.426. We are 95% confident that the true odds ratio will fall into (0.325, 0.558).
```{r}
Baltimore_reg %>% 
  broom::tidy() %>% 
  filter(term == "victim_sexMale") %>%
  mutate(
    OR = exp(estimate),
    lower_CI = exp(estimate - 1.96 * std.error),
    upper_CI = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, lower_CI, upper_CI) %>% 
  knitr::kable(digits = 3)
```

### Regression for Each City ? 


homicide_df %>% 
  drop_na(victim_age, victim_race, victim_sex) %>% 
  mutate(victim_age = as.numeric(victim_age)) %>% 
  nest(df = -city_state) %>% 
    mutate(
    models = map(.x = df, ~glm(status_numeric ~ victim_race + victim_age + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
    )
    


## Problem 3
There's no na in the data set. I converted baby sex, female and male races to factor variables, inches to centimeters, and grams to pounds.
```{r,results='hide'}
birthwt_df =
  read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>% 
  mutate(
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    babysex = as.factor(babysex),
    malform = as.factor(malform)) 
  
  
map(birthwt_df, ~sum(is.na(.)))
```
### Model proposal 

I would like to propose a model using baby's head circumference, mother's weight gain during pregnancy, and baby's length.

Data visualization for bwt and the variables I'm choosing. There isn't extreme skewness below and I do not need to do transformation to the variables.
```{r}
birthwt_df %>% 
  ggplot(aes(x = bwt)) + 
  geom_density()

birthwt_df %>% 
  ggplot(aes(x = bhead)) + 
  geom_density()

birthwt_df %>% 
  ggplot(aes(x = blength)) + 
  geom_density()

birthwt_df %>% 
  ggplot(aes(x = wtgain)) + 
  geom_density()
```

The residual against fitted value plot indicate that the residuals are approximately constant around residual = 0 line.
```{r}
model_1 = lm(bwt ~ bhead + blength + wtgain, data = birthwt_df)
```

```{r}
modelr::add_residuals(birthwt_df, model_1) %>% 
  ggplot(aes(x = bwt, y = resid)) +
  geom_point(alpha = .3)
```


